### 2023-05-19 README.Rmd
remove old block of code setting default filter size; no longer required; updated README link

`dataaimsr` is provided by the [Australian Institute of Marine Science](https://www.aims.gov.au) under the MIT License ([MIT](https://opensource.org/licenses/MIT)).

>>>>

`dataaimsr` is provided by the [Australian Institute of Marine Science](https://www.aims.gov.au) under the MIT License ([MIT](https://opensource.org/license/mit/)).
